---
title: "Mindfullness Calendar"
author: "Andrew Purgiel"
date: "11/17/2021"
output:
  pdf_document:
    fig_width: 5.25
    fig_height: 4.25

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, eval = TRUE)
```

```{r, eval = TRUE}
library(png)
library(tidyverse)
library(ggpubr)
library(gridExtra)
library(lubridate)
```


# import data
```{r}
df <- read_csv("./song_list_csv.csv")
```

# check that there is a movie title for each movie song
```{r, eval = TRUE}


movie_songs <- df %>%
  filter(wd == "Sunday")

check <- df %>%
  filter(!is.na(movie))
  
  
  # #randomize order
  # sample(size = length(.))

```

# make date/weekday df
```{r}

day_df <- 
  data.frame(
    date = seq(
  ymd("2023-01-01"), 
  ymd("2023-12-31"),
  by = '2 days')
  ) %>%
  mutate( wd = weekdays(date))


```


# assign birthday, sundays, and special other dates?
# assign movie song to every other Sunday
```{r}
# date df of every other sunday
dates_sun <- day_df %>%
  filter(wd == "Sunday")

odd_sun_rows <- seq(1, nrow(dates_sun), 2)

dates_sun <- dates_sun[odd_sun_rows, ]



# make dfs without special days
songs_filt <- df %>%
  filter(title != "In Da Club") %>% # w/o birthday song
  filter(wd != "Sunday" | is.na(wd)) %>% # w/o movie songs
  select(-wd)


days_filt <- day_df %>%
  filter(date != "2023-01-22") %>% # w/o birthday
  filter( !(date %in% pull(dates_sun, date))) # w/o every 4th sunday

df_filt <- songs_filt %>%
  cbind(days_filt)%>%
  #randomize row order
  mutate(date = sample(date))




# identify birthday song
bday <- df %>%
    filter(title == "In Da Club") %>%
  mutate(date = ymd("2023-01-22"))


# make dataframe of sunday songs
sun_songs <- df %>%
    filter(title != "In Da Club") %>% # don't include birthday song
  filter(wd == "Sunday") %>%
  select(-wd)


sundays <- dates_sun %>%
  cbind(sun_songs) %>%
  #randomize row order
  mutate(date = sample(date))

# make final df
df_final <- df_filt %>%
  rbind(sundays, bday) %>%
  select(date, everything()) %>%
  arrange(date)

```


* set parameters for plots
```{r}

# from calendar code
sheet_width <- 5.25
sheet_height <- 4.25


# text sizes
small <- 6
xsmall <- small/1.5
medium <- small*1.5
large <- small*2
xlarge <- small *8

```


* layout sheets
** date, lyrics on one side
** song, artist, and movie on other side
** apply to each row
```{r, fig.width=sheet_width,  fig.height=sheet_height}


  make_sheets <- function(row_num) {

    # pick out one row of data
    a <- df_final[row_num, ]

  b <- a %>%
  # add return in line if more than 50 char in line
  # https://stackoverflow.com/questions/2351744/insert-line-breaks-in-long-string-word-wrap
  mutate(lyrics = paste(strwrap(lyrics,36), collapse="\n"))

#  lyrics and date page
 pg1 <-  ggplot(b)+
    geom_text( x = 0.5, y = 0.9,
             hjust = 0.5, vjust = 1,
             size = medium,
             aes(label = month.abb[month(date)]))+
    geom_text( x = 0.5, y = 0.75,
             hjust = 0.5, vjust = 1,
             size = xlarge,
             aes(label = day(date)))+
  # add note for cinema sunday
  {if(!is.na(b$movie))geom_text( x = 0.1, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = large, angle = 55,label = "Cinema")
    }+
  {if(!is.na(b$movie))geom_text( x = 0.9, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = large, angle = -55,label = "Sunday")
    }+
      geom_text( x = 0.5, y = 0.17,
             hjust = 0.5, vjust = 0.5,
             size = small,
             aes(label = dQuote(lyrics)))+
   theme_bw()
 
  print(pg1)

#answer page
pg2 <- ggplot(b)+
      geom_text( x = 0.5, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = xsmall,
             aes(label = paste("Song:", title)))+
  # add movie title if it is cinema sunday
               {if(!is.na(b$movie))geom_text( x = 0.5, y = 0.4,
             hjust = 0.5, vjust = 1,
             size = xsmall,
             aes(label = paste("Movie:", movie)))
               }+
      geom_text( x = 0.5, y = 0.5,
             hjust = 0.5, vjust = 1,
             size = xsmall,
             aes(label = paste("Artist:", artist)))+
     theme_bw()

print(pg2)
}


# make pdf file of calendar
 

pdf("test_file.pdf", width = 5.25, height = 4.25)
 
    #plot cover page
ggplot(b)+
    geom_text( x = 0.5, y = 0.5,
             hjust = 0.5, vjust = 0,
             size = medium,
             label = 'The Semi-Daily\n"What the heck is that Song?"\n Calendar')+
        geom_text( x = 0.025, y = 0.1,
             hjust = 0, vjust = 0,
             size = xsmall,
             label = paste0("Instructions:\n\n",
             "Guess the song and artist from which the lyrics originate.\n",
                            "For Cinema Sundays, ",
                            "guess what movie the song is from as well.\n",
                            "Answers are on the back of each page.")
                            )+
  theme_bw()
  
# plot all other pages
  for(x in rownames(df_final)) make_sheets(x) %>% print()

  
  dev.off()


 
 # Example for how to print pdf row by row:
  # from https://stackoverflow.com/questions/46007357/generating-a-pdf-document-for-every-row -------
# 
# canada <- c(100, 80, 100, 100, 20)
# korea <- c(100, 80, 100, 26, 65)
# brazil <- c(100, 90, 100, 30, 30)
# fruit <- rbind(canada, korea, brazil)
# colnames(fruit) <- c("apple", "orange", "banana", "grape", "kiwi")
# fruit
# 
# price <- function(val){
# 
#   val <- tolower(val)
#   myrow <- fruit[val,]
#   nation <- tools::toTitleCase(val)
#   score.min <- c(myrow)[which.min(c(myrow))]
# 
#   cat(paste0("In ", nation, " cheapest fruit costs ", score.min, " cents."))
# 
# }
# 
# 
# 
# write_lines_pdf <- function(x, file = "pdffile", ...) {
#     if (!grepl("\\.pdf$", file)) file <- paste0(file, ".pdf") # append .pdf if not present
#     pdf(file)
#     plot.new()
#     text(x = 0, y = 1, labels = paste(x, collapse = "\n"), adj = c(0, 1), ...)   
#     dev.off()
# }
# 
# for(nm in rownames(fruit)) write_lines_pdf(capture.output(price(nm)), nm)


```


# make rach_plot list
```{r, eval = FALSE}
plots <- map(rach_df[], function(x){


  data <- x
  ggplot(data)+
  geom_tile(aes(x = 0, y = 2.55, width = 0.75, height = 1,
                fill = if (!is.na(pic)) pic else 'white'),
            color = 'black', size = 1)+
  geom_text(aes(label = task),
            x = 0, y = 1.95, vjust = 1, hjust = 0.5,
            size = 3
            )+
    theme_classic()+
  coord_cartesian(xlim = c(-1,1), ylim = c(0,3.5))+
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      plot.margin=unit(c(-0.1,-.05,-0.4,-.05), "in"),
      legend.position = 'none',
      panel.background = element_rect(fill = 'lightcyan')
    )+
    labs(x = NULL, y = NULL)+
    scale_fill_identity()

}
)

plots_blank2 <- map(rach_df[c(1:2)], function(x){

  data <- x
  ggplot(data)+
    theme_classic()+
    coord_cartesian(xlim = c(-1,1), ylim = c(0,3.5))+
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      plot.margin=unit(c(-0.1,-.05,-0.4,-.05), "in"),
      panel.background = element_rect(fill = 'lightcyan')
    )+
    labs(x = NULL, y = NULL)
  
}
)



# plots <- map(rach_df[], function(x){
# 
#   task_text <- x$task[1]
#   # taskexp <- x$task[1]
#   # footexp <- x$foot[1]
#   # noted <- as.character(expression(paste(taskexp, footexp)))
#   # parse_choice <- if(is.na(x$foot[1])) F else T
# 
#   data <- x
#   ggplot(data)+
#   geom_tile(aes(x = 0, y = 0, width = 1, height = 2))+
#     theme_classic()+
#   coord_cartesian(xlim = c(-1,1), ylim = c(-1,1))+
#     theme(
#       axis.text = element_blank(),
#       axis.title = element_text(size = 8),
#       axis.ticks = element_blank(),
#       axis.line = element_blank(),
#       # plot.margin=unit(c(-0.5,0,-0.5,0), "in")
#     )+
#     labs(x = task_text, y = NULL)
# 
# }
# )

# ggarrange(plots[1], plots[2], ncol = 3)

plots_with_space <- c(plots[c(1:35)], plots_blank2,
                      plots[c(36:41)], plots_blank2,
                      plots[c(42:length(plots))])
```


# make rach cal pdf
```{r, eval = FALSE}

# fo variable in expression
# https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r


  
pdf('rach_cal.pdf', width = rach_width, height = rach_height)


   do.call('grid.arrange', c(plots_with_space, list(ncol = 8)))

dev.off()







```

# put image in each box test
```{r, eval = FALSE}
img <- readPNG(system.file("img", "Rlogo.png", package="png"))
g <- grid::rasterGrob(img, interpolate=TRUE)

plots <- map(rach_df[c(1:10)], function(x){


  data <- x
  ggplot(data)+
  geom_tile(aes(x = 0, y = 2.55, width = 1, height = 1),
            fill = NA, color = 'black')+
      annotation_custom(g, xmin=-0.5, xmax=0.5, ymin=2.05, ymax=3.05) +
  geom_text(aes(label = task ),
            x = 0, y = 2, vjust = 1, hjust = 0.5,
            size = 5
            )+
    theme_classic()+
  coord_cartesian(xlim = c(-1,1), ylim = c(0,3.5))+
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      plot.margin=unit(c(-0.5,0,-0.5,0), "in")
    )+
    labs(x = NULL, y = NULL)

}
)

pdf('test_img.pdf', width = rach_width, height = rach_height)


   do.call('grid.arrange', c(plots, list(ncol = 8)))

dev.off()
```

# make rach_cal image
```{r, eval = FALSE }

png('rach_cal.png', width = rach_width, height = rach_height, units = 'in', res = 220)

   do.call('grid.arrange', c(plots_with_space, list(ncol = 8)))

dev.off()
```


#combine cal and title images
```{r, eval = FALSE}



cal_img <- readPNG('rach_cal.png')
background <- grid::rasterGrob(cal_img, interpolate=TRUE)

title_img <- readPNG('title_rach.png')
title <- grid::rasterGrob(title_img, interpolate=TRUE)


pdf('rach_cal_final.pdf', width = rach_width, height = rach_height)

ggplot()+
  annotation_custom(background, xmin=-12, xmax=12, ymin=-12, ymax=12)+
  coord_cartesian(xlim = c(-12,12), ylim = c(-12,12))+
  theme(
    plot.margin=unit(c(-1,-1,-1,-1), "in")
  )+
  annotation_custom(title, xmin=-3, xmax=3, ymin=-.2, ymax=3.5)
  # geom_text(label = 'TEEEST', aes(x = 0, y = 1), size = 10, font)

dev.off()


```

