---
title: "Mindfullness Calendar"
author: "Andrew Purgiel"
date: "11/17/2021"
output:
  pdf_document:
    fig_width: 7
    fig_height: 7
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, eval = TRUE)
```

```{r, eval = TRUE}
library(png)
library(tidyverse)
library(ggpubr)
library(gridExtra)
library(lubridate)
```


# import data
```{r}
df <- read_csv("./song_list_csv.csv")
```

# check that there is a movie title for each movie song
```{r, eval = TRUE}


movie_songs <- df %>%
  filter(wd == "Sunday")

check <- df %>%
  filter(!is.na(movie))
  
  
  # #randomize order
  # sample(size = length(.))

```

# make date/weekday df
```{r}

day_df <- 
  data.frame(
    date = seq(
  ymd("2023-01-01"), 
  ymd("2023-12-31"),
  by = '2 days')
  ) %>%
  mutate( wd = weekdays(date))


```


# assign birthday, sundays, and special other dates?
# assign movie song to every other Sunday
```{r}
# date df of every other sunday
dates_sun <- day_df %>%
  filter(wd == "Sunday")

odd_sun_rows <- seq(1, nrow(dates_sun), 2)

dates_sun <- dates_sun[odd_sun_rows, ]



# make dfs without special days
songs_filt <- df %>%
  filter(title != "In Da Club") %>% # w/o birthday song
  filter(wd != "Sunday" | is.na(wd)) %>% # w/o movie songs
  select(-wd)


days_filt <- day_df %>%
  filter(date != "2023-01-22") %>% # w/o birthday
  filter( !(date %in% pull(dates_sun, date))) # w/o every 4th sunday

df_filt <- songs_filt %>%
  cbind(days_filt)%>%
  #randomize row order
  mutate(date = sample(date))




# identify birthday song
bday <- df %>%
    filter(title == "In Da Club") %>%
  mutate(date = ymd("2023-01-22"))


# make dataframe of sunday songs
sun_songs <- df %>%
    filter(title != "In Da Club") %>% # don't include birthday song
  filter(wd == "Sunday") %>%
  select(-wd)


sundays <- dates_sun %>%
  cbind(sun_songs) %>%
  #randomize row order
  mutate(date = sample(date))

# make final df
df_final <- df_filt %>%
  rbind(sundays, bday) %>%
  select(date, everything()) %>%
  arrange(date)

```


* set parameters for plots
```{r}

# from calendar code
sheet_width <- 5.25
sheet_height <- 4.25


# text sizes
small <- 8
medium <- small*1.5
large <- small*2
xlarge <- small *8

```


* layout sheets
** date, lyrics on one side
** song, artist, and movie on other side
```{r, fig.width=sheet_width,  fig.height=sheet_height}

a <- df_final[1,]


b <- a %>%
  # add return in line if more than 50 char in line
  # https://stackoverflow.com/questions/2351744/insert-line-breaks-in-long-string-word-wrap
  mutate(lyrics = paste(strwrap(lyrics,50), collapse="\n"))


ggplot(b)+
    geom_text( x = 0.5, y = 1,
             hjust = 0.5, vjust = 1,
             size = medium,
             aes(label = month.abb[month(date)]))+
  geom_text( x = 0.5, y = 0.8,
             hjust = 0.5, vjust = 1,
             size = xlarge,
             aes(label = day(date)))+
    geom_text( x = 0.5, y = 0.8,
             hjust = 0.5, vjust = 1,
             size = xlarge,
             aes(label = day(date)))+
  # add note for cinema sunday
  {if(!is.na(b$movie))geom_text( x = 0.1, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = large, angle = 55,label = "Cinema")
    }+
  {if(!is.na(b$movie))geom_text( x = 0.9, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = large, angle = -55,label = "Sunday")
    }+
      geom_text( x = 0.5, y = 0.27,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = dQuote(lyrics)))

plot.new()

#answer
ggplot(b)+
      geom_text( x = 0.5, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = paste("Song:", title)))+
  # add movie title if it is cinema sunday
               {if(!is.na(b$movie))geom_text( x = 0.5, y = 0.4,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = paste("Movie:", movie)))
               }+
      geom_text( x = 0.5, y = 0.5,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = paste("Artist:", artist)))
plot.new()

  
```


* apply to each row
```{r, fig.width=sheet_width,  fig.height=sheet_height}

a <- df_final[1:2,]


make_sheets <- function(x) {


  b <- x %>%
  # add return in line if more than 50 char in line
  # https://stackoverflow.com/questions/2351744/insert-line-breaks-in-long-string-word-wrap
  mutate(lyrics = paste(strwrap(lyrics,50), collapse="\n"))

  pdf("test_file.pdf")

 pg1 <- ggplot(b)+
    geom_text( x = 0.5, y = 1,
             hjust = 0.5, vjust = 1,
             size = medium,
             aes(label = month.abb[month(date)]))+
  geom_text( x = 0.5, y = 0.8,
             hjust = 0.5, vjust = 1,
             size = xlarge,
             aes(label = day(date)))+
    geom_text( x = 0.5, y = 0.8,
             hjust = 0.5, vjust = 1,
             size = xlarge,
             aes(label = day(date)))+
  # add note for cinema sunday
  {if(!is.na(b$movie))geom_text( x = 0.1, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = large, angle = 55,label = "Cinema")
    }+
  {if(!is.na(b$movie))geom_text( x = 0.9, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = large, angle = -55,label = "Sunday")
    }+
      geom_text( x = 0.5, y = 0.27,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = dQuote(lyrics)))

 print(pg1)

#answer
ggplot(b)+
      geom_text( x = 0.5, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = paste("Song:", title)))+
  # add movie title if it is cinema sunday
               {if(!is.na(b$movie))geom_text( x = 0.5, y = 0.4,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = paste("Movie:", movie)))
               }+
      geom_text( x = 0.5, y = 0.5,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = paste("Artist:", artist)))

dev.off()

}

  a %>%
  rowwise() %>%
  make_sheets()


 # note, if I don't use print() func, I get no pages in pdf
  # but I how separate pages?
 
  
  
  make_sheets <- function(dat, row_num) {

    # pick out one row of data
    a <- dat[row_num, ]

  b <- a %>%
  # add return in line if more than 50 char in line
  # https://stackoverflow.com/questions/2351744/insert-line-breaks-in-long-string-word-wrap
  mutate(lyrics = paste(strwrap(lyrics,50), collapse="\n"))

  pdf("test_file.pdf")

 pg1 <- ggplot(b)+
    geom_text( x = 0.5, y = 1,
             hjust = 0.5, vjust = 1,
             size = medium,
             aes(label = month.abb[month(date)]))+
  geom_text( x = 0.5, y = 0.8,
             hjust = 0.5, vjust = 1,
             size = xlarge,
             aes(label = day(date)))+
    geom_text( x = 0.5, y = 0.8,
             hjust = 0.5, vjust = 1,
             size = xlarge,
             aes(label = day(date)))+
  # add note for cinema sunday
  {if(!is.na(b$movie))geom_text( x = 0.1, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = large, angle = 55,label = "Cinema")
    }+
  {if(!is.na(b$movie))geom_text( x = 0.9, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = large, angle = -55,label = "Sunday")
    }+
      geom_text( x = 0.5, y = 0.27,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = dQuote(lyrics)))

 print(pg1)

#answer
ggplot(b)+
      geom_text( x = 0.5, y = 0.6,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = paste("Song:", title)))+
  # add movie title if it is cinema sunday
               {if(!is.na(b$movie))geom_text( x = 0.5, y = 0.4,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = paste("Movie:", movie)))
               }+
      geom_text( x = 0.5, y = 0.5,
             hjust = 0.5, vjust = 1,
             size = small,
             aes(label = paste("Artist:", artist)))

dev.off()

}

  price <- function(val){

  val <- tolower(val)
  myrow <- fruit[val,]
  nation <- tools::toTitleCase(val)
  score.min <- c(myrow)[which.min(c(myrow))]

  cat(paste0("In ", nation, " cheapest fruit costs ", score.min, " cents."))

}



write_lines_pdf <- function(x, file = "pdffile", ...) {
    if (!grepl("\\.pdf$", file)) file <- paste0(file, ".pdf") # append .pdf if not present
    pdf(file)
    plot.new()
    text(x = 0, y = 1, labels = paste(x, collapse = "\n"), adj = c(0, 1), ...)   
    dev.off()
}

for(nm in rownames(fruit)) write_lines_pdf(capture.output(price(nm)), nm)

 
 


canada <- c(100, 80, 100, 100, 20)
korea <- c(100, 80, 100, 26, 65)
brazil <- c(100, 90, 100, 30, 30)
fruit <- rbind(canada, korea, brazil)
colnames(fruit) <- c("apple", "orange", "banana", "grape", "kiwi")
fruit

price <- function(val){

  val <- tolower(val)
  myrow <- fruit[val,]
  nation <- tools::toTitleCase(val)
  score.min <- c(myrow)[which.min(c(myrow))]

  cat(paste0("In ", nation, " cheapest fruit costs ", score.min, " cents."))

}



write_lines_pdf <- function(x, file = "pdffile", ...) {
    if (!grepl("\\.pdf$", file)) file <- paste0(file, ".pdf") # append .pdf if not present
    pdf(file)
    plot.new()
    text(x = 0, y = 1, labels = paste(x, collapse = "\n"), adj = c(0, 1), ...)   
    dev.off()
}

for(nm in rownames(fruit)) write_lines_pdf(capture.output(price(nm)), nm)


```


# make rach_plot list
```{r, eval = TRUE}
plots <- map(rach_df[], function(x){


  data <- x
  ggplot(data)+
  geom_tile(aes(x = 0, y = 2.55, width = 0.75, height = 1,
                fill = if (!is.na(pic)) pic else 'white'),
            color = 'black', size = 1)+
  geom_text(aes(label = task),
            x = 0, y = 1.95, vjust = 1, hjust = 0.5,
            size = 3
            )+
    theme_classic()+
  coord_cartesian(xlim = c(-1,1), ylim = c(0,3.5))+
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      plot.margin=unit(c(-0.1,-.05,-0.4,-.05), "in"),
      legend.position = 'none',
      panel.background = element_rect(fill = 'lightcyan')
    )+
    labs(x = NULL, y = NULL)+
    scale_fill_identity()

}
)

plots_blank2 <- map(rach_df[c(1:2)], function(x){

  data <- x
  ggplot(data)+
    theme_classic()+
    coord_cartesian(xlim = c(-1,1), ylim = c(0,3.5))+
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      plot.margin=unit(c(-0.1,-.05,-0.4,-.05), "in"),
      panel.background = element_rect(fill = 'lightcyan')
    )+
    labs(x = NULL, y = NULL)
  
}
)



# plots <- map(rach_df[], function(x){
# 
#   task_text <- x$task[1]
#   # taskexp <- x$task[1]
#   # footexp <- x$foot[1]
#   # noted <- as.character(expression(paste(taskexp, footexp)))
#   # parse_choice <- if(is.na(x$foot[1])) F else T
# 
#   data <- x
#   ggplot(data)+
#   geom_tile(aes(x = 0, y = 0, width = 1, height = 2))+
#     theme_classic()+
#   coord_cartesian(xlim = c(-1,1), ylim = c(-1,1))+
#     theme(
#       axis.text = element_blank(),
#       axis.title = element_text(size = 8),
#       axis.ticks = element_blank(),
#       axis.line = element_blank(),
#       # plot.margin=unit(c(-0.5,0,-0.5,0), "in")
#     )+
#     labs(x = task_text, y = NULL)
# 
# }
# )

# ggarrange(plots[1], plots[2], ncol = 3)

plots_with_space <- c(plots[c(1:35)], plots_blank2,
                      plots[c(36:41)], plots_blank2,
                      plots[c(42:length(plots))])
```


# make rach cal pdf
```{r}

# fo variable in expression
# https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r


  
pdf('rach_cal.pdf', width = rach_width, height = rach_height)


   do.call('grid.arrange', c(plots_with_space, list(ncol = 8)))

dev.off()







```

# put image in each box test
```{r}
img <- readPNG(system.file("img", "Rlogo.png", package="png"))
g <- grid::rasterGrob(img, interpolate=TRUE)

plots <- map(rach_df[c(1:10)], function(x){


  data <- x
  ggplot(data)+
  geom_tile(aes(x = 0, y = 2.55, width = 1, height = 1),
            fill = NA, color = 'black')+
      annotation_custom(g, xmin=-0.5, xmax=0.5, ymin=2.05, ymax=3.05) +
  geom_text(aes(label = task ),
            x = 0, y = 2, vjust = 1, hjust = 0.5,
            size = 5
            )+
    theme_classic()+
  coord_cartesian(xlim = c(-1,1), ylim = c(0,3.5))+
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      plot.margin=unit(c(-0.5,0,-0.5,0), "in")
    )+
    labs(x = NULL, y = NULL)

}
)

pdf('test_img.pdf', width = rach_width, height = rach_height)


   do.call('grid.arrange', c(plots, list(ncol = 8)))

dev.off()
```

# make rach_cal image
```{r}

png('rach_cal.png', width = rach_width, height = rach_height, units = 'in', res = 220)

   do.call('grid.arrange', c(plots_with_space, list(ncol = 8)))

dev.off()
```


#combine cal and title images
```{r, eval = TRUE}



cal_img <- readPNG('rach_cal.png')
background <- grid::rasterGrob(cal_img, interpolate=TRUE)

title_img <- readPNG('title_rach.png')
title <- grid::rasterGrob(title_img, interpolate=TRUE)


pdf('rach_cal_final.pdf', width = rach_width, height = rach_height)

ggplot()+
  annotation_custom(background, xmin=-12, xmax=12, ymin=-12, ymax=12)+
  coord_cartesian(xlim = c(-12,12), ylim = c(-12,12))+
  theme(
    plot.margin=unit(c(-1,-1,-1,-1), "in")
  )+
  annotation_custom(title, xmin=-3, xmax=3, ymin=-.2, ymax=3.5)
  # geom_text(label = 'TEEEST', aes(x = 0, y = 1), size = 10, font)

dev.off()


```


# create 2719 df
```{r}

foco_df <- list(

    data.frame(task = "Ask a stranger\na stupid question.", foot = NA, pic = 'cyan', other = F),
    data.frame(task = "Trade someone a shiny.", foot = NA, pic = 'cyan', other = F),
    data.frame(task = "Jump in some cold water.\nNot in the bathtub.\n<61.9 deg F.", foot = NA, pic = 'cyan', other = F),
    data.frame(task = "Climb so hard you 'psaaaaaaat.'\nWith at least 5 A's.", foot = NA, pic = 'cyan', other = F),
    data.frame(task = "Watch a Disney movie.", foot = NA, pic = 'cyan', other = F),

    data.frame(task = "Make or buy a pizzaball.", foot = NA, pic = 'cyan', other = F),
    data.frame(task = "Find a really good new meme.\nAt least as good as\nbaguetti and meatballs.", foot = NA, pic = 'cyan', other = F),  

    data.frame(task = "Do something Goggins would do.\nPlease avoid passing out\nor pissing blood.", foot = NA, pic = 'cyan', other = F),
    data.frame(task = "Do/attempt a cartweel.", foot = NA, pic = 'cyan', other = F),
    data.frame(task = "Climb blindfolded.", foot = NA, pic = 'cyan', other = F),    
    data.frame(task = "Make a pancake >18 inches\nin diameter. Or a\nwaffle, but those suck.", foot = NA, pic = 'cyan', other = F),

    data.frame(task = "Teach someone some trad stuff.", foot = NA, pic = 'cyan', other = F),
    
     data.frame(task = "Learn a new dance.", foot = NA, pic = 'cyan', other = F),
    
    data.frame(task = "Sing karaoke at a bar.", foot = NA, pic = 'cyan', other = F),
    
 
    

    
  
    
    
    
  
  data.frame(task = "List 5 things about yourself\nthat are pretty rad.", foot = NA, pic = 'deepskyblue', other = F),
  data.frame(task = "Name one thing you'll do\ntomorrow better than\nyou did today.", foot = NA, pic = 'deepskyblue', other = F),
   data.frame(task = "List 10 things you're\nthankful for.", foot = NA, pic = 'deepskyblue', other = F),
  data.frame(task = "Note 5 things in your yard\nyou've never\nnoticed before.", foot = NA, pic = 'deepskyblue', other = F),
  
  
  
  data.frame(task = "Forgive yourself for\nsomething you've done.", foot = NA, pic = 'deepskyblue', other = F),

  
    data.frame(task = "Reflect on your day\nfor 15 minutes.", foot = NA, pic = 'deepskyblue', other = F),  

    data.frame(task = "Do something purely for\nthe nostalgia.", foot = NA, pic = 'deepskyblue', other = F),  
       data.frame(task = "Watch or listen to 15 min\neach of 'conservative'\nand 'liberal' news.", foot = NA, pic = 'deepskyblue', other = F),  
  data.frame(task = "Do something you never\ngot the chance\nto do as a kid.", foot = NA, pic = 'deepskyblue', other = F),
  data.frame(task = "Tell someone the weird-ass\ndream you had last night.", foot = NA, pic = 'deepskyblue', other = F),  
data.frame(task = "Do some yoga.", foot = NA, pic = 'deepskyblue', other = F),  
    data.frame(task = "Do some sauna.\nDouble points if\n>325 deg F", foot = NA, pic = 'deepskyblue', other = F),   
    data.frame(task = "Go for a half-hour walk.\nNo 14ers or running,\nya bastards.", foot = NA, pic = 'deepskyblue', other = F),
    data.frame(task = "Don't step in motorized\nvehicle today.\nYes, truckbeds are cheating.", foot = NA, pic = 'deepskyblue', other = F),    
    
    data.frame(task = "Buy something at a brick+mortar\nstore that you'd usually\nbuy on Amazon.", foot = NA, pic = 'deepskyblue', other = F),

  
  
  data.frame(task = "Forgive someone for\nsomething they've done.", foot = NA, pic = 'palevioletred1', other = F),
  data.frame(task = "Tell someone why you're\nhappy they're in your life.\nCrying encouraged.", foot = NA, pic = 'palevioletred1', other = F),  
  data.frame(task = "Complement a stranger.", foot = NA, pic = 'palevioletred1', other = F),    
  data.frame(task = "Call someone you haven't\nspoken to in a while.", foot = NA, pic = 'palevioletred1', other = F),    
  data.frame(task = "Perform a random act\nof kindness\nfor a stranger.", foot = NA, pic = 'palevioletred1', other = F),  
  data.frame(task = "Mail someone a letter for\nno apparent reason.", foot = NA, pic = 'palevioletred1', other = F),
  data.frame(task = "Volunteer for at least 15 min.\n(Try Access Fund\ngroups in CO).", foot = NA, pic = 'palevioletred1', other = F),
     data.frame(task = "Spend an hour on a\ngift for someone.", foot = NA, pic = 'palevioletred1', other = F),    
    data.frame(task = "Learn something about\nsomeone you met today.\nMore than just name.", foot = NA, pic = 'palevioletred1', other = F),  
  
  




  data.frame(task = "Cook something you've never\ncooked before. Just using\na new sauce don't count", foot = NA, pic = 'chocolate1', other = F),

    data.frame(task = "Throw a snowball at someone.", foot = NA, pic = 'chocolate1', other = F),

  data.frame(task = "Tell an inside joke that no\none who's present will get.", foot = NA, pic = 'chocolate1', other = F),
  
     data.frame(task = "Don't say an unneeded\n'like' for an entire day.", foot = NA, pic = 'chocolate1', other = F),  
  
  data.frame(task = "Watch the sunset\nfrom start to finish\nwithout going blind.", foot = NA, pic = 'chocolate1', other = F),

  
  
  
 data.frame(task = "Try something stupid spicy.\nWithout killing yourself.\nOr throwing up, please.", foot = NA, pic = 'plum2', other = F),
 data.frame(task = "Get some DQ.", foot = NA, pic = 'plum2', other = F),
    data.frame(task = "Have a vegan day.\nOnly ocunts if you brag\nabout being a better person.", foot = NA, pic = 'plum2', other = F),    
    data.frame(task = "Go a day without cheese.\nYou can make up\nfor it tomorrow.", foot = NA, pic = 'plum2', other = F), 
    data.frame(task = "Bake something from scratch.", foot = NA, pic = 'plum2', other = F),


    data.frame(task = "Attend a restaurant for\nthe first time.\nA new Chipotle doesn't count.", foot = NA, pic = 'plum2', other = F),
    
        data.frame(task = "Have a vegtarian meal when\n eating out for dinner.\nChiptole doesn't count.", foot = NA, pic = 'plum2', other = F),
    data.frame(task = "Eat a meal with the 2719\ncrew all together.", foot = NA, pic = 'plum2', other = F),  



  data.frame(task = "Spend some time cleaning\nthe house. Extra points\nif bathtub included.", foot = NA, pic = 'seagreen1', other = F),
data.frame(task = "Turn your phone off\nfor 24 hours.", foot = NA, pic = 'seagreen1', other = F),
  data.frame(task = "Go 24 hours without talking.", foot = NA, pic = 'seagreen1', other = F),  
    data.frame(task = "Don't swear for an hour.", foot = NA, pic = 'seagreen1', other = F),
    data.frame(task = "Don't swear after 5pm.", foot = NA, pic = 'seagreen1', other = F),
    data.frame(task = "Don't swear for day.\nGood luck.", foot = NA, pic = 'seagreen1', other = F),  
  data.frame(task = "Don't watch any video\nstreaming service today.", foot = NA, pic = 'seagreen1', other = F), 
  
  
  
  
  
  data.frame(task = "Drive alone with no music or\nphone for 20 minutes.", foot = NA, pic = 'rosybrown1', other = F),
  data.frame(task = "Listen to a genre of music you\ntypically don't listen to.", foot = NA, pic = 'rosybrown1', other = F),     
  data.frame(task = "Check out some live music.", foot = NA, pic = 'rosybrown1', other = F),
  data.frame(task = "Listen to a song while doing\nabsolutely nothing else.", foot = NA, pic = 'rosybrown1', other = F),
     data.frame(task = "Dance to a song when\nyou're by yourself.", foot = NA, pic = 'rosybrown1', other = F),
   data.frame(task = "Dance to a song\nwith someone else.", foot = NA, pic = 'rosybrown1', other = F),
   data.frame(task = "COMPLETELY BELT OUT a song\n when you're by yourself.", foot = NA, pic = 'rosybrown1', other = F),  
   data.frame(task = "Sing (or try to sing) a song\nfrom start to finish.", foot = NA, pic = 'rosybrown1', other = F),
   data.frame(task = "Share a song with someone who\nyou think will like it.", foot = NA, pic = 'rosybrown1', other = F),
  data.frame(task = "Make a song verse,\n or a poem, I guess...\nVerse sounds cooler.", foot = NA, pic = 'rosybrown1', other = F),  
     data.frame(task = "Freestyle for at least 10 seconds\nBARS.", foot = NA, pic = 'rosybrown1', other = F),
  
  
  
  data.frame(task = "Play some Pizzaball.", foot = NA, pic = 'orangered1', other = F),
  data.frame(task = "Play some dice. YARRRRR!", foot = NA, pic = 'orangered1', other = F),
  data.frame(task = "Complete a puzzle.\nHas to have a difficulty level\nof at least 7.", foot = NA, pic = 'orangered1', other = F),
    data.frame(task = "Have a fire.\nNo lighter fluid, dammit.", foot = NA, pic = 'orangered1', other = F),
    data.frame(task = "Play videogames as a group.\nBonus points if you yell at TV.", foot = NA, pic = 'orangered1', other = F),
    data.frame(task = "Play trivia.\nOnly counts\nif team name is good.", foot = NA, pic = 'orangered1', other = F),
    data.frame(task = "Have wine and cheese night.\nYes, cheesesticks still count.", foot = NA, pic = 'orangered1', other = F),
    data.frame(task = "Have a Bob Ross night.", foot = NA, pic = 'orangered1', other = F),    data.frame(task = "Go on a date.\nDate with Josh doesn't count.\nSorry Josh.", foot = NA, pic = 'orangered1', other = F),    

  
  

    data.frame(task = "Complete a task that\nyou've failed at previously.", foot = NA, pic = 'yellow1', other = F),  
  data.frame(task = "Check box because you were\ntoo lazy to do a task today.", foot = NA, pic = 'yellow1', other = F),  
  data.frame(task = "Check box because you\nforgot to do a task today.", foot = NA, pic = 'yellow1', other = F),
  data.frame(task = "Check box because\nyou attempted and\nfailed a task today.", foot = NA, pic = 'yellow1', other = F),
     data.frame(task = "Let me know what is\nthe stupidest/ridiculousest\ntask on here.", foot = NA, pic = 'yellow1', other = F),
     data.frame(task = "Complete one of the old\nmindful tasks you\nnever completed.", foot = NA, pic = 'yellow1', other = F) 
)
  #randomize order
  sample(size = length(.))

```


# make foco_plot list
```{r, eval = TRUE}

# # fo variable in expression
# # https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
# 
# plots <- map(foco_df[], function(x){
# 
#   taskexp <- x$task[1]
#   footexp <- x$foot[1]
#   noted <- bquote(.(taskexp)~(mu*M))
#   # parse_choice <- if(is.na(x$foot[1])) F else T
# 
#   data <- x
#   ggplot(data)+
#   geom_tile(aes(x = 0, y = 2.55, width = 0.75, height = 1),
#             fill = NA, color = 'black')+
#   geom_text(aes(label = if(is.na(foot)) task else task ),
#             x = 0, y = 2, vjust = 1, hjust = 0.5,
#             size = 5,
#             # parse = parse_choice
#             )+
#     theme_classic()+
#   coord_cartesian(xlim = c(-1,1), ylim = c(0,3.5))+
#     theme(
#       axis.text = element_blank(),
#       axis.title = element_blank(),
#       axis.ticks = element_blank(),
#       axis.line = element_blank(),
#       plot.margin=unit(c(-0.4,0,-0.5,0), "in")
#     )+
#     labs(x = NULL, y = NULL)
# 
# }
# )


plots <- map(foco_df[], function(x){


data <- x
  ggplot(data)+
  geom_tile(aes(x = 0, y = 2.55, width = 0.75, height = 1,
                fill = if (!is.na(pic)) pic else 'white'),
            color = 'black', size = 1)+
  geom_text(aes(label = task),
            x = 0, y = 1.95, vjust = 1, hjust = 0.5,
            size = 3
            )+
    theme_classic()+
  coord_cartesian(xlim = c(-1,1), ylim = c(0,3.5))+
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      plot.margin=unit(c(-0.1,-.05,-0.4,-.05), "in"),
      legend.position = 'none',
      panel.background = element_rect(fill = 'lightcyan')
    )+
    labs(x = NULL, y = NULL)+
    scale_fill_identity()

}
)

plots_blank2 <- map(foco_df[c(1:2)], function(x){

  data <- x
  ggplot(data)+
    geom_blank()+
    theme_classic()+
    coord_cartesian(xlim = c(-1,1), ylim = c(0,3.5))+
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      plot.margin=unit(c(-0.1,-.05,-0.4,-.05), "in"),
      panel.background = element_rect(fill = 'lightcyan')
    )+
    labs(x = NULL, y = NULL)
  
}
)



plots_with_space <- c(plots[c(1:35)], plots_blank2,
                      plots[c(36:41)], plots_blank2,
                      plots[c(42:length(plots))])
```

# create 2719 cal pdf
```{r, eval = FALSE}

pdf('foco_cal.pdf', width = foco_width, height = foco_height)


   do.call('grid.arrange', c(plots_with_space, list(ncol = 8)))

dev.off()

```


# make foco_cal image
```{r}

png('foco_cal.png', width = foco_width, height = foco_height, units = 'in', res = 220)

   do.call('grid.arrange', c(plots_with_space, list(ncol = 8)))

dev.off()
```



#combine cal and title images
```{r, eval = TRUE}



cal_img <- readPNG('foco_cal.png')
background <- grid::rasterGrob(cal_img, interpolate=TRUE)

title_img <- readPNG('title_foco.png')
title <- grid::rasterGrob(title_img, interpolate=TRUE)


pdf('foco_cal_final.pdf', width = rach_width, height = rach_height)

ggplot()+
  annotation_custom(background, xmin=-12, xmax=12, ymin=-12, ymax=12)+
  coord_cartesian(xlim = c(-12,12), ylim = c(-12,12))+
  theme(
    plot.margin=unit(c(-1,-1,-1,-1), "in")
  )+
  annotation_custom(title, xmin=-3, xmax=3, ymin=-.5, ymax=3.2)
  # geom_text(label = 'TEEEST', aes(x = 0, y = 1), size = 10, font)

dev.off()


```

# test image fr printing
```{r}
test_print <-
  ggplot()+
  geom_text(aes(x = 0, y=0), label = 'This is a test.', size = 64)+
  coord_cartesian(xlim = c(-12, 12), ylim = c(-4,4))+
  theme_void()


pdf('test_print.pdf', width = 17, height = 8)

test_print

dev.off()

```

